\MakeUppercase{The Structure of $k$-Planar Graphs}

### 2020-03-26 k-planar.tex
Done with reviewers comments

  Let $X_H:=\{x\in V(H): Z\cap Y_x\neq\emptyset\}$.  The connectivity of $G[Z]$ implies that $H[X_H]$ is connected.
  %Property~\tref{ancestor-edge} implies that, for every $xy\in E(H)$, one of $x$ or $y$ is a $T$-ancestor of the other.
  Choose $a(v)\in X_H$ to be any member of $X_H$ that does not have a strict $T$-ancestor in $X_H$.  Transitivity of the $T$-ancestor relationship, \tref{ancestor-edge}, and connectivity of $H[X_H]$ implies that $a(v)$ is a $T$-ancestor of every node $x\in X_H$, as required.
\end{proof}

@@

@@

Next we show that $\mathcal{S}$ has small layered width with respect to the layering $\mathcal{L}=\langle L_1,\ldots,L_h\rangle$:

@@

>>>>

  Let $X_H:=\{x\in V(H): Z\cap Y_x\neq\emptyset\}$.  The connectivity of $G[Z]$ implies that $H[X_H]$ is connected.
  %Property~\tref{ancestor-edge} implies that, for every $xy\in E(H)$, one of $x$ or $y$ is a $T$-ancestor of the other.
  Choose $a(v)\in X_H$ to be the member of $X_H$ that does not have a strict $T$-ancestor in $X_H$.  Transitivity of the $T$-ancestor relationship, \tref{ancestor-edge}, and connectivity of $H[X_H]$ implies that such an $a(v)$ exists and is a $T$-ancestor of every node $x\in X_H$, as required.
\end{proof}

@@

From this point onward, the plan is to show that
\begin{enumerate}[(i)]
  \item $\mathcal{S}$ has small layered width with respect to the layering $\mathcal{L}$ and that
  \item $J$ has small treewidth.
\end{enumerate}

First we need to understand the relationship between sets $S_x\in\mathcal{S}$ and the related sets objects $Y_x$, $V_x$, $F_x$, and $N_x$.

@@

Next we complete Step~(i) and show that $\mathcal{S}$ has small layered width with respect to the layering $\mathcal{L}=\langle L_1,\ldots,L_h\rangle$:

@@

% From this point onward, the plan is to show that (i)~$\mathcal{S}$ has small layered width with respect to a $\mathcal{L}$ and that (ii)~$J$ has small treewidth.

\snote{Reviewer \#2 writes: \emph{Lemma 3: the property (T2) is sth peculiar; EVERY tree-decomposition of H has the property that if x and y are adjacent then the root of x and the root of y are comparable in the tree; I suggest to get rid of this one. The same story applies to Claim 4 where the authors give an elaborate proof of that fact again.} The reviewer is right about Lemma~3 (the other reviewer noticed it also) but not Claim~4.  In Claim~4, $T$ is the tree in a tree decomposition of $H$.  At this point we're setting up to show that $T$ can also be used to get a tree decomposition of $J$ without blowing up the width too much.

To address this, I've added the map breaking things down into Step~(i) and Step~(ii), and the following text.}

We now proceed with Step~(ii), showing that $J$ has small treewidth. To accomplish this, we construct a small width tree-decomposition $\mathcal{C}:=(C_x:x\in V(T))$ of $J$ using the same tree $T$ used in the tree decomposition $\mathcal{T}:=(B_x:x\in V(T))$ of $H$.  The following claim will be useful in showing that the resulting decomposition has small width.
